---
title: "QMM Assignment 2"
author: "SAI SREE PULIMAMIDI"
date: "2022-10-18"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
tbl <- matrix(c(22,14,30,600,100 ,
16,20,24,625,120,
80,60,70,"-","-" ), ncol=5, byrow=TRUE)
colnames(tbl) <- c("Warehouse 1", "Warehouse 2", "Warehouse 3","Production cost","Production Capacity")
rownames(tbl) <- c("Plant A", "Plant B","Monthly Demand")
tbl <- as.table(tbl)
tbl
```
LP format of transporation problem are

$$ \text{Min} \hspace{.2cm} TC = 22 x_{11} +14 x_{12} +30 x_{13}$$
$$\hspace{2cm}+16 x_{21}+20 x_{22}+ 24 x_{23}$$
$$\hspace{2cm}+80 x_{31}+ 60 x_{32}+ 70 x_{33}$$

The Supply constraints are :

$$x_{11} + x_{12} + x_{13}\le 100$$
$$x_{21} + x_{22} + x_{23}\le 120$$

$$\text The Demand Constraints are :$$

$$x_{11} +x_{21}\ge 80$$
$$x_{12} +x_{22}\ge 60$$
$$x_{13} +x_{23}\ge 70$$

$${\ Non-Negativity\ constraints}$$

$$x_{ij}\ge 0$$ \text{where}$$ i= 1,2,3$$ \text{and}$$j= 1,2,3$$

```{r}
library(lpSolve)

# Set up cost matrix

cost_tbl <- matrix(c(622,614,630,0,
641,645,649,0), ncol = 4,byrow = TRUE)

# Set Plant names

colnames(cost_tbl ) <- c("Warehouse 1", "Warehouse 2","Warehouse 3","Dummy")
rownames(cost_tbl ) <- c("Plant A", "Plant B")
cost_tbl 
```

#Set up constraint signs and right-hand sides (supply side)

```{r}
row.signs <- rep("<=", 2)
row.rhs <- c(100,120)
```

#Demand (sinks) side constraints

```{r}
col.signs <- rep(">=", 4)
col.rhs <- c(80,60,70,10)
```

#Running the 

```{r}
lptrans_tbl <- lp.transport(cost_tbl, "min", row.signs, row.rhs, col.signs, col.rhs)
```

#Values of all 8 variables

```{r}
lptrans_tbl$solution
```

#Value of the objective function

```{r}
lptrans_tbl$objval
```

#Getting the constraints value

```{r}
lptrans_tbl$solution
```

2) Dual Problem:

Formulating the dual constraints and variables
$$
\text{The objective function is }Max\hspace{.3cm} VA= 80w_{1}+60w_{2}+70w_{3}-100p_{1}-120p_{2}
$$
$$
\text{Where,}\hspace{.3cm}w_{1}\text{= Price received at the Warehouse 1}
$$
$$
 w_{2}\text{= Price, received at the Warehouse 2}
$$
$$
w_{3}\text{= Price, received at the Warehouse 3}
$$
$$
 p_{1}\text{= Price, purchased at the Plant A}
$$
$$
 p_{2}\text{= Price, purchased at the Plant B}
$$
Subject to:
$$w_{1}-p_{1} \ge 622$$
$$w_{2}-p_{1} \ge 614$$
$$w_{3}-p_{1} \ge 630$$
$$w_{1}-p_{2} \ge 641$$
$$w_{2}-p_{2} \ge 645$$
$$w_{3}-p_{2} \ge 649
$$
3) Economic Interpretation of dual:

 The goal of AED's business is to reduce the total cost of production and shipment.

 To achieve this, the corporation needs hire a logistic company to handle the transportation, which will include purchasing the AEDs and transporting them to various warehouses in an effort to reduce the overall cost of production and shipping.

$$
\text{The constraints in the dual can be modified as}$$
$$w_{1} \ge 622+p_{1}$$
$$w_{2} \ge 614+p_{1}$$
$$w_{3} \ge 630+p_{1}$$
$$w_{1} \ge 641+p_{2}$$
$$w_{2} \ge 645+p_{2}$$
$$w_{3} \ge 649+p_{2}
$$
$$ \text{From the above we get to see that}\hspace{.3cm} w_{1}−p_{1}\ge 622$$
$$ \text{That can be exponented as}\hspace{.3cm} w_{1} \ge 622+p_{1}$$
$$ \text{Here}\hspace{.3cm} w_{1}\hspace{.3cm}\text{is considered as the price payments being received at the origin which is nothing else,but the revenue,whereas}\hspace{.3cm} p_{1}+622\hspace{.3cm}\text{is the money paid at the origin at PlantA}
$$
$$\text{This can be formulated as below}\\
MR \ge MC
$$

$$
\text{If MR < MC, in order to meet the Marginal Revenue (MR), we need to decrease the costs at the plants.}$$
$$\text{If MR > MC, in order to meet the Marginal Revenue (MR), we need to increase the production supply.}$$
$$\text{For a profit maximization, The Marginal Revenue(MR) should be equal to MarginalCosts(MC)}$$
$$\text{Therefore, MR=MC}$$
$$\text{Based on above interpretation, we can conclude that,profit maximization takes place if MC is equal to MR.}
$$

